# ***Vintage Data Analysis by Ramakrishna B***
##1. First we need to load the excell data into R.
### Install and load package readxl.

```{r}
library("readxl");
library(dplyr)
library(stringr);
library(ggplot2);
```

##2. Now define the path and load the vintage file into R.

```{r}
path = "C:/Users/rbellana/Desktop";
setwd(path);
getwd();
vintage <- read_excel("Vintage Art V2.1.xlsx",sheet = "Art-i-stick");
head(vintage);
```

##3. Now studying the data.
```{r}
dim(vintage);   
names(vintage); 
str(vintage);  
head(vintage);
```

##4. Now we want to split the height and widht of the Art Piece size.
```{r}
s = str_split(vintage$"Art Piece Size ", "X");
head(s);
```
			 #####Sample for spliting.
                  #a = "2 X 3";      
                  #s = str_split(a,"X")
				  
				  
##5. Now extracting width and height elements of the column separately. So we use User Defined functions.
```{r}
get_x= function(ele){
              ele[1]
}
get_y= function(ele){
              ele[2]
}
```

### Applying user defined function for the entire column.
```{r}
x=sapply(s,FUN=get_x);
y=sapply(s,FUN=get_y);
head(x)
head(y)
```

## 6. We are getting as "17in. ",where "in." and space is not required.
```{r}
x = str_replace(x,"in. "," ");
y = str_replace(y,"in."," ");
```

##7. Now remove the spaces using trim function.
```{r}
x = str_trim(x);
y = str_trim(y);
```

##8.Now change into integer from character form.
```{r}
vintage$x = as.integer(x)
vintage$Y = as.integer(y)
```

##9. Column names should be like one word.So replace space with "_".
```{r}
names(vintage) = str_trim(names(vintage));
names(vintage) = str_replace_all(names(vintage)," ","_");
```


##10. Now arranging the data with X on X axis and y on Y axis
```{r}
vintage = arrange(vintage,x,y);
```

##11. Now analyzing the height and width of the paints done on basis of brush size and painter.
```{r}
g3 = ggplot(data= vintage,aes(x=x,y=y,size=vintage$Brush_Size,color=vintage$Brush_Size));
g3 = g3 + geom_point();
g3 = g3 + facet_grid(.~Top_3_artists);  
print(g3);
```

##12.
```{r}
names(vintage)
print(g4)
```


##13. Top 3 Artistist
```{r}
unique(vintage$"Top_3_artists")
t = table(vintage$"Top_3_artists")
barplot(sort(t),horiz = T)
```{r}

##14.Count of art by Artists:
### default "stat" for "bars" is 'bin" that gives the count value
```{r}
g = ggplot(data=vintage,aes(x=vintage$"Top_3_artists"))
g = g +  geom_bar(stat="bin",fill= "blue",position ="stack",color = "red");
g = g + geom_bar(width = 0.5,fill= topo.colors(5),color="darkgreen");
g = g + coord_flip();
print(g)
```

##15.when the data contains y values in a column, use stat="identity".
```{r}
df = data.frame(x=1:3,y=11:13)
g = g + ggplot(df,aes(x=x,y=y));
g = g + geom_bar(stat = "identity")
print(g)
```

##16. Count the "IsGood_Purchase" per Artist.
### weighted column should be numeric to that value, so that we can sum up together.
```{r}
g1 = ggplot(data=vintage,aes(x=vintage$"Top_3_artists"),weight = vintage$"IsGood_Purchase");
g1 = g1 + geom_bar(width=0.5);
g1 = g1 + coord_flip();
print(g1);
```

##17.Art Nationality
```{r}
g2 = ggplot(data=vintage,aes(x=vintage$"Art_Nationality"));
g2 = g2 + geom_bar(width=0.5,stat = "bin",fill=topo.colors(5));
g2 = g2 + coord_flip();
print(g2);
```

### Bin data--> Missing values are currently sliently dropped.

##18.count of arts per prominent colour with data labels
```{r}
freq = table(vintage$"Prominent_Color")
names(freq)
str(freq)
pos = freq + 200
df = data.frame(Poss);
t = data.frame(vintage$"prominent_Color");
head(vintage$"Prominent_Color")
```

```{r}
names(iris);
iris$"Species"
Poss= table(iris$"Species") + 400;
d = merge(vintage, df, by.x="prominent_Color",by.y= "Var1")
```





